### 2019-04-05 0_abstract.tex
Tweak abstract.

\begin{abstract}
% 128 words
We present Task Bench, a \emph{parameterized} benchmark designed to
explore the performance envelopes of parallel and distributed
programming systems under a variety of application scenarios. Task
Bench seeks to provide the ease of implementation and portability of
microbenchmarks, which makes comparisons between many systems
possible, with the ability to model a wide range of application
scenarios, giving it coverage approximating mini-apps.

>>>>

\begin{abstract}
% 128 words
We present Task Bench, a \emph{parameterized} benchmark designed to
explore the performance envelopes of parallel and distributed
programming systems under a variety of application scenarios. Task
Bench seeks to combine the ease of implementation and portability of
microbenchmarks, which makes comparisons between many systems
possible, with the ability to model a wide range of application
scenarios that distill the key characteristics of larger applications.
